Group L3-T-2
\begin{itemize}
    \item Samuel Dewan
    \item Sujeevani Pujari 
    \item Mario Shebib 
    \item Morgan Smith
\end{itemize}

\subsection{About Us}

As COVID-19 concerns bring everyday life all over the world to a standstill, our
team consisting of Carleton Engineering students, works towards tackelling these
challenges and make life easier for consumers everywhere.

\subsection{The Team Project} 

As Governments proceed to re-open workplaces, how effective are the risk
management protocols implemented by employers? Are employers prepared for the
employees to come back? How can we be more aware and not panic in implementing
proper entry way guidelines to eliminate the risk of COVID-19? As consumers
around the world face these challenges everyday, our team works towards
providing the ultimate solution to following proper call-in procedures. We bring
to you a system that looks after the well being of your employees and follows
government regulated infection prevention policies, practices and guidelines for
workplaces. 

This Project will be designed to meet the needs of the employers to look after
the safety of their employees. Our groundbreaking access control system complies
with employer standards and provides employees access to a COVID-19 free
workplace. As studies show that fever ($<$ 39.1 °C) is the most frequent symptom
in more than 50\% of COVID-19 cases \cite{Michelen_2020}, our system prevents
entry to employees that present symptoms of COVID-19. Additionally, our system
adheres to social distancing guidelines implied by the government and restricts
access to reduce the spread of COVID-19. With many more features and benefits,
implementing our system at workplaces around the world, successfully helps in
providing a COVID-19 free work environment for employees. 

\subsection{Project Features}

Our revolutionary access control system will:
\begin{itemize}
    \item Display a green light at the entrance if it is accepting people
    \item Be equipped with an NFC (Near Field Communication) security badge
          reader
          the reader 
    \item Recognize the employee based on their NFC security badge presented to
    \item Measure the body temperature of an employee trying to enter the work
          premises 
    \item Prevent access to employees with body temperature over 39.1 °C
    \item Keep track of employee details such as their body temperature
          measurement for last 14 days, based on a unique user NFC security badge
          user ID
    \item Identifies the number of people in the premises 
    \item Dispalys a red light at the entrance to restricts access when the
          maximum threshold of the premises has been acquired
\end{itemize}

