\subsection{Timeline}

Table \ref{table:timeline} shows important submission deadlines and when we plan
to have major milestones completed.

\begin{table}[!hbt]
\renewcommand\arraystretch{1.4}\arrayrulecolor{LightSteelBlue3}
\captionsetup{singlelinecheck=false, font=blue, labelfont=sc, labelsep=quad}
\caption{Timeline}\vskip -1.5ex
\begin{tabular}{@{\,}r <{\hskip 2pt} !{\foo} >{\raggedright\arraybackslash}p{10cm}}
\toprule
\addlinespace[1.5ex]
2020-10-02 & Submission: Project Proposal\\
2020-10-11 & Milestone: Complete Initial Research\\
2020-10-23 & Submission: Project Design\\
2020-11-08 & Milestone: Complete Hardware Interface Code\\
2020-11-15 & Milestone: Complete Hardware Communication Code\\
2020-11-22 & Milestone: Complete Application Code\\
2020-11-25 & Submission: Code Peer Review\\
2020-12-09 & Submission: Final Report\\
\end{tabular}
\label{table:timeline}
\end{table}

\subsection{Milestones}

\paragraph{Complete Initial Research}
By this point we should have completed all of out research in order to select
what hardware and libraries we would like to use for our project.

\paragraph{Complete Hardware Interface Code}
By this point all of the code responsible for interfacing with hardware and all
of the associated test stubs and applications should be complete. Work on this
milestone can be done in parallel with work on the communication and application
code.

\paragraph{Complete Communication Code}
By this point all of the code for exchanging information between nodes and all
of the associated test stubs and applications should be complete. Work on this
milestone can be done in parallel with work on the hardware interface and
application code.

\paragraph{Complete Application Code}
By this point all of the application level code should be complete and we should
be performing integration testing of our complete system. Work on this milestone
can be cone in parallel with work on the hardware interface and communication
code.

