% Copyright (C) 2020 by Morgan Smith
% Copyright (C) 2020 by Sunjeevani Pujari

\subsection{Motivation}

Our access control system is designed to help employers look after the safety
of their employees.  This system provides employers with an access control
system that grants access to the workplace based on a security badge and
measured body temperature.  Additionally, our system helps building owners
adhere to social distancing guidelines by tracking the number of people on the
premises and restricting users from entering the building when the maximum
threshold for the building has been attained.  Although not in the scope of the
project, our system would work with employers to comply with their standards
and constraints to provide their employees access to a COVID-19 free workplace.
Our system aims to enable a COVID-19 free work environment.


\subsection{Design}

Our product is made up of two parts: the control server, and the door nodes.
Our product interacts with two types of actors: Operators and Users.

The control server maintains a database of door nodes, user profiles, and
interaction logs.  The control server also runs a GUI that can be used to
interact with the system. This GUI can be used to modify user profiles and the
list of door nodes. The GUI can also be used to modify system settings such as
the maximum occupancy limit and the maximum allowable body temperature.

When a user attempts to use a door node, their identity is checked against
their user profile.  Each interaction with a door node is recorded in a user
log.

The design is further detailed in the class diagrams found in appendix
\ref{sec:appendix}.

\subsection{Functional Requirements}

The  functional requirements for the system are listed below:

\begin{itemize}
	\item Display a  light at the entrance if it is accepting people
	\item Be equipped with a Near Field Communication (NFC) security badge
	reader
	\item Recognize employees based on their NFC security cards presented to
	the reader 
	\item Measure the body temperature of an employee trying to enter the work
	premises 
	\item Prevent access to employees with a fever
	\item Track and limit the maximum number of people in the building and display a
	light at the entrance when the building has acquired maximum threshold
\end{itemize}
